Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-07-28 main-sketch.tex
update figures

\begin{figure}[ht]
\begin{center}
\centering
  \subfigure[Data set sizing from $300$ to $800$ ]{

    \label{subsubsec_vs_datasize1adir}
  }
  \subfigure[Data set sizing from $14000$ to $20000$]{

  \label{subsubsec_vs_datasize1bdir}} 
\caption{With $\betad(1,1)$ prior distribution, Unbalanced datasets of mean $(0.2,0.3, 0.5)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize_dir}
\end{center}
\end{figure}

>>>>

\begin{figure}[ht]
\begin{center}
\centering
  \subfigure[Data set sizing from $300$ to $800$ ]{
    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_300_dirichlet.eps}
    \label{subsubsec_vs_datasize1adir}
  }
  \subfigure[Data set sizing from $14000$ to $20000$]{
     \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_1k_dirichelt.eps}   
  \label{subsubsec_vs_datasize1bdir}} 
\caption{Increasing data size with fixed $\dirichlet(1,1,1)$ prior distribution, Unbalanced datasets of mean $(0.2,0.3, 0.5)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize_dir}
\end{center}
\end{figure}
